---
title: "ChessMF"
author: "Toetu"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Here, I am analyzing the effects of Mental Fatigue (MF) on expert chess players during a game of chess. The data sets that we will be analyzing are the 1948 FIDE world chess championship, and the 2022 candidates games. We will be using the 'Hyper2' package developed by Dr. Hankin. 

```{r}
library(hyper2)
library(readxl)

#Data
Fide1948 <- read_excel("~/Academic Life/Master of Analytics/ENGE817 STEM Research paper/Fide1948.xlsx")
View(Fide1948)

#We have 5 players that played 50 games all together
#How many possible games of 2 can occur for 5 players?
factorial(5)/factorial(5 - 2)

```

#Hyper2 object
```{r}
fide48 <- c(
#Ewue VS Keres
EuwW_lostTo_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
EuwW_beats_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
EuwW_draws_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
KerW_lostTo_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
KerW_beats_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
KerW_draws_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
EuwW_lostTo_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
EuwW_beats_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
EuwW_draws_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
KerW_lostTo_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
KerW_beats_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
KerW_draws_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],

#Smyslov VS Reshevsky
SmyW_lostTo_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
SmyW_beats_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
SmyW_draws_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
ResW_lostTo_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
ResW_beats_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
ResW_draws_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
SmyW_lostTo_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
SmyW_beats_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
SmyW_draws_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
ResW_lostTo_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
ResW_beats_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
ResW_draws_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],

#Botvinnik VS Euwe
BotW_lostTo_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
BotW_beats_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
BotW_draws_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
EuwW_lostTo_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
EuwW_beats_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
EuwW_draws_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
BotW_lostTo_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
BotW_beats_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
BotW_draws_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
EuwW_lostTo_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
EuwW_beats_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
EuwW_draws_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],

#--------------------------------------------------------------------------------------------------------------------------

#Ewue VS Reshevsky
EuwW_lostTo_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
EuwW_beats_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
EuwW_draws_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
ResW_lostTo_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
ResW_beats_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
ResW_draws_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
EuwW_lostTo_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
EuwW_beats_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
EuwW_draws_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
ResW_lostTo_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
ResW_beats_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
ResW_draws_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Euwe" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],

#Smyslov VS Keres
SmyW_lostTo_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
SmyW_beats_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
SmyW_draws_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
KerW_lostTo_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
KerW_beats_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
KerW_draws_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
SmyW_lostTo_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
SmyW_beats_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
SmyW_draws_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
KerW_lostTo_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
KerW_beats_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
KerW_draws_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],

#Botvinnik VS Smyslov
BotW_lostTo_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
BotW_beats_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
BotW_draws_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
SmyW_lostTo_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
SmyW_beats_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
SmyW_draws_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
BotW_lostTo_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
BotW_beats_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
BotW_draws_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Smyslov" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
SmyW_lostTo_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
SmyW_beats_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
SmyW_draws_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],

#--------------------------------------------------------------------------------------------------------------------------

#Ewue VS Smyslov
EuwW_lostTo_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer == "Smyslov" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
EuwW_beats_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer == "Smyslov" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
EuwW_draws_Smy_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer == "Smyslov" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
SmyW_lostTo_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer == "Euwe" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
SmyW_beats_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer == "Euwe" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
SmyW_draws_Euw_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer == "Euwe" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
EuwW_lostTo_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer == "Smyslov" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
EuwW_beats_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer == "Smyslov" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
EuwW_draws_Smy_MF = dim(Fide1948[Fide1948$WhitePlayer == "Euwe" & Fide1948$BlackPlayer == "Smyslov" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
SmyW_lostTo_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer == "Euwe" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
SmyW_beats_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer == "Euwe" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
SmyW_draws_Euw_MF = dim(Fide1948[Fide1948$WhitePlayer == "Smyslov" & Fide1948$BlackPlayer == "Euwe" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],

#Reshevsky VS Botvinnik
ResW_lostTo_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer == "Botvinnik" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
ResW_beats_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer == "Botvinnik" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
ResW_draws_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer == "Botvinnik" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
BotW_lostTo_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer == "Reshevsky" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
BotW_beats_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer == "Reshevsky" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
BotW_draws_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer == "Reshevsky" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
ResW_lostTo_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer == "Botvinnik" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
ResW_beats_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer == "Botvinnik" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
ResW_draws_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer == "Botvinnik" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
BotW_lostTo_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer == "Reshevsky" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
BotW_beats_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer == "Reshevsky" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
BotW_draws_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer == "Reshevsky" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],

#Botvinnik VS Keres
BotW_lostTo_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
BotW_beats_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
BotW_draws_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
KerW_lostTo_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
KerW_beats_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
KerW_draws_Bot_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
BotW_lostTo_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
BotW_beats_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
BotW_draws_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Botvinnik" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
KerW_lostTo_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
KerW_beats_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
KerW_draws_Bot_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Botvinnik" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],

#Reshevsky VS Keres
ResW_lostTo_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
ResW_beats_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
ResW_draws_Ker_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
KerW_lostTo_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0 & Fide1948$Moves < 40,])[1],
KerW_beats_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 1 & Fide1948$Moves < 40,])[1],
KerW_draws_Res_NMF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0.5 & Fide1948$Moves < 40,])[1],
ResW_lostTo_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
ResW_beats_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
ResW_draws_Ker_MF = dim(Fide1948[Fide1948$WhitePlayer == "Reshevsky" & Fide1948$BlackPlayer== "Keres" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1],
KerW_lostTo_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0 & Fide1948$Moves >= 40,])[1],
KerW_beats_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 1 & Fide1948$Moves >= 40,])[1],
KerW_draws_Res_MF = dim(Fide1948[Fide1948$WhitePlayer == "Keres" & Fide1948$BlackPlayer== "Reshevsky" & Fide1948$White == 0.5 & Fide1948$Moves >= 40,])[1]

)
#---------------------------------------------------------------------------------------------------------------------------
```



**Hyper 2 object**
```{r}
results <- as.list(fide48)
attach(results)
H <- hyper2()

# Ewue VS Keres
Ewue_vs_Keres <- c("Ewue","Keres","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Ewue"  ,"white"), Ewue_vs_Keres, EuwW_beats_Ker_NMF)
H <- H + trial(c("Keres","white"), Ewue_vs_Keres, KerW_beats_Euw_NMF)
H <- H + trial(  "Keres"           , Ewue_vs_Keres, EuwW_lostTo_Ker_NMF)
H <- H + trial(  "Ewue"           , Ewue_vs_Keres, KerW_lostTo_Euw_NMF)
H <- H + trial(  "draw"             , Ewue_vs_Keres, EuwW_draws_Ker_NMF)
H <- H + trial(  "draw"             , Ewue_vs_Keres, KerW_draws_Euw_NMF)

#MF
H <- H + trial(c("Ewue"  ,"white","MF"), Ewue_vs_Keres, EuwW_beats_Ker_MF)
H <- H + trial(c("Keres","white","MF"), Ewue_vs_Keres, KerW_beats_Euw_MF)
H <- H + trial(  c("Keres","MF")           , Ewue_vs_Keres, EuwW_lostTo_Ker_MF)
H <- H + trial(  c("Ewue","MF")           , Ewue_vs_Keres, KerW_lostTo_Euw_MF)
H <- H + trial(  c("draw","MF")            , Ewue_vs_Keres, EuwW_draws_Ker_MF)
H <- H + trial(  c("draw","MF")            , Ewue_vs_Keres, KerW_draws_Euw_MF)

#Smyslov VS Reshevsky
Smyslov_vs_Reshevsky <- c("Smyslov","Reshevsky","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Smyslov"  ,"white"), Smyslov_vs_Reshevsky, SmyW_beats_Res_NMF)
H <- H + trial(c("Reshevsky","white"), Smyslov_vs_Reshevsky, ResW_beats_Smy_NMF)
H <- H + trial(  "Reshevsky"           , Smyslov_vs_Reshevsky, SmyW_lostTo_Res_NMF)
H <- H + trial(  "Smyslov"           , Smyslov_vs_Reshevsky, ResW_lostTo_Smy_NMF)
H <- H + trial(  "draw"              , Smyslov_vs_Reshevsky, SmyW_draws_Res_NMF)
H <- H + trial(  "draw"              , Smyslov_vs_Reshevsky, ResW_draws_Smy_NMF)

#MF
H <- H + trial(c("Smyslov"  ,"white","MF"), Smyslov_vs_Reshevsky, SmyW_beats_Res_MF)
H <- H + trial(c("Reshevsky","white","MF") , Smyslov_vs_Reshevsky, ResW_beats_Smy_MF)
H <- H + trial(  c("Reshevsky","MF")           , Smyslov_vs_Reshevsky, SmyW_lostTo_Res_MF)
H <- H + trial(  c("Smyslov","MF")           , Smyslov_vs_Reshevsky, ResW_lostTo_Smy_MF)
H <- H + trial(  c("draw","MF")            , Smyslov_vs_Reshevsky, SmyW_draws_Res_MF)
H <- H + trial(  c("draw","MF")            , Smyslov_vs_Reshevsky, ResW_draws_Smy_MF)

#Botvinnik VS Euwe
Botvinnik_vs_Euwe <- c("Botvinnik","Euwe","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Botvinnik"  ,"white"), Botvinnik_vs_Euwe, BotW_beats_Euw_NMF)
H <- H + trial(c("Euwe","white"), Botvinnik_vs_Euwe, EuwW_beats_Bot_NMF)
H <- H + trial(  "Euwe"           , Botvinnik_vs_Euwe, BotW_lostTo_Euw_NMF)
H <- H + trial(  "Botvinnik"           , Botvinnik_vs_Euwe, EuwW_lostTo_Bot_NMF)
H <- H + trial(  "draw"              , Botvinnik_vs_Euwe, EuwW_draws_Bot_NMF)
H <- H + trial(  "draw"              , Botvinnik_vs_Euwe, BotW_draws_Euw_NMF)

#MF
H <- H + trial(c("Botvinnik"  ,"white","MF"), Botvinnik_vs_Euwe, BotW_beats_Euw_MF)
H <- H + trial(c("Euwe","white","MF") , Botvinnik_vs_Euwe, EuwW_beats_Bot_MF)
H <- H + trial(  c("Euwe","MF")           , Botvinnik_vs_Euwe, BotW_lostTo_Euw_MF)
H <- H + trial(  c("Botvinnik","MF")           , Botvinnik_vs_Euwe, EuwW_lostTo_Bot_MF)
H <- H + trial(  c("draw","MF")            , Botvinnik_vs_Euwe, EuwW_draws_Bot_MF)
H <- H + trial(  c("draw","MF")            , Botvinnik_vs_Euwe, BotW_draws_Euw_MF)
#=========================================================================================================
#=========================================================================================================
#Ewue VS Reshevsky
Ewue_vs_Reshevsky <- c("Ewue","Reshevsky","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Ewue"  ,"white"), Ewue_vs_Reshevsky, EuwW_beats_Res_NMF)
H <- H + trial(c("Reshevsky","white"), Ewue_vs_Reshevsky, ResW_beats_Euw_NMF)
H <- H + trial(  "Reshevsky"           , Ewue_vs_Reshevsky, EuwW_lostTo_Res_NMF)
H <- H + trial(  "Ewue"           , Ewue_vs_Reshevsky, ResW_lostTo_Euw_NMF)
H <- H + trial(  "draw"             , Ewue_vs_Reshevsky, EuwW_draws_Res_NMF)
H <- H + trial(  "draw"             , Ewue_vs_Reshevsky, ResW_draws_Euw_NMF)

#MF
H <- H + trial(c("Ewue"  ,"white","MF"), Ewue_vs_Reshevsky, EuwW_beats_Res_MF)
H <- H + trial(c("Reshevsky","white","MF"), Ewue_vs_Reshevsky, ResW_beats_Euw_MF)
H <- H + trial(  c("Reshevsky","MF")           , Ewue_vs_Reshevsky, EuwW_lostTo_Res_MF)
H <- H + trial(  c("Ewue","MF")           , Ewue_vs_Reshevsky, ResW_lostTo_Euw_MF)
H <- H + trial(  c("draw","MF")            , Ewue_vs_Reshevsky, EuwW_draws_Res_MF)
H <- H + trial(  c("draw","MF")            , Ewue_vs_Reshevsky, ResW_draws_Euw_MF)

#Smyslov VS Keres
Smyslov_vs_Keres <- c("Smyslov","Keres","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Smyslov"  ,"white"), Smyslov_vs_Keres, SmyW_beats_Ker_NMF)
H <- H + trial(c("Keres","white"), Smyslov_vs_Keres, KerW_beats_Smy_NMF)
H <- H + trial(  "Keres"           , Smyslov_vs_Keres, SmyW_lostTo_Ker_NMF)
H <- H + trial(  "Smyslov"           , Smyslov_vs_Keres, KerW_lostTo_Smy_NMF)
H <- H + trial(  "draw"              , Smyslov_vs_Keres, SmyW_draws_Ker_NMF)
H <- H + trial(  "draw"              , Smyslov_vs_Keres, KerW_draws_Smy_NMF)

#MF
H <- H + trial(c("Smyslov"  ,"white","MF"), Smyslov_vs_Keres, SmyW_beats_Ker_MF)
H <- H + trial(c("Keres","white","MF") , Smyslov_vs_Keres, KerW_beats_Smy_MF)
H <- H + trial(  c("Keres","MF")           , Smyslov_vs_Keres, SmyW_lostTo_Ker_MF)
H <- H + trial(  c("Smyslov","MF")           , Smyslov_vs_Keres, KerW_lostTo_Smy_MF)
H <- H + trial(  c("draw","MF")            , Smyslov_vs_Keres, SmyW_draws_Ker_MF)
H <- H + trial(  c("draw","MF")            , Smyslov_vs_Keres, KerW_draws_Smy_MF)

#Botvinnik VS Smyslov
Botvinnik_vs_Smyslov <- c("Botvinnik","Smyslov","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Botvinnik"  ,"white"), Botvinnik_vs_Smyslov, BotW_beats_Smy_NMF)
H <- H + trial(c("Smyslov","white"), Botvinnik_vs_Smyslov, SmyW_beats_Bot_NMF)
H <- H + trial(  "Smyslov"           , Botvinnik_vs_Smyslov, BotW_lostTo_Smy_NMF)
H <- H + trial(  "Botvinnik"           , Botvinnik_vs_Smyslov, SmyW_lostTo_Bot_NMF)
H <- H + trial(  "draw"              , Botvinnik_vs_Smyslov, SmyW_draws_Bot_NMF)
H <- H + trial(  "draw"              , Botvinnik_vs_Smyslov, BotW_draws_Smy_NMF)

#MF
H <- H + trial(c("Botvinnik"  ,"white","MF"), Botvinnik_vs_Smyslov, BotW_beats_Smy_MF)
H <- H + trial(c("Smyslov","white","MF") , Botvinnik_vs_Smyslov, SmyW_beats_Bot_MF)
H <- H + trial(  c("Smyslov","MF")           , Botvinnik_vs_Smyslov, BotW_lostTo_Smy_MF)
H <- H + trial(  c("Botvinnik","MF")           , Botvinnik_vs_Smyslov, SmyW_lostTo_Bot_MF)
H <- H + trial(  c("draw","MF")            , Botvinnik_vs_Smyslov, SmyW_draws_Bot_MF)
H <- H + trial(  c("draw","MF")            , Botvinnik_vs_Smyslov, BotW_draws_Smy_MF)
#=========================================================================================================
#=========================================================================================================
#Ewue VS Smyslov
Ewue_vs_Smyslov <- c("Ewue","Smyslov","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Ewue"  ,"white"), Ewue_vs_Smyslov, EuwW_beats_Smy_NMF)
H <- H + trial(c("Smyslov","white"), Ewue_vs_Smyslov, SmyW_beats_Euw_NMF)
H <- H + trial(  "Smyslov"           , Ewue_vs_Smyslov, EuwW_lostTo_Smy_NMF)
H <- H + trial(  "Ewue"           , Ewue_vs_Smyslov, SmyW_lostTo_Euw_NMF)
H <- H + trial(  "draw"             , Ewue_vs_Smyslov, EuwW_draws_Smy_NMF)
H <- H + trial(  "draw"             , Ewue_vs_Smyslov, SmyW_draws_Euw_NMF)

#MF
H <- H + trial(c("Ewue"  ,"white","MF"), Ewue_vs_Smyslov, EuwW_beats_Smy_MF)
H <- H + trial(c("Smyslov","white","MF"), Ewue_vs_Smyslov, SmyW_beats_Euw_MF)
H <- H + trial(  c("Smyslov","MF")           , Ewue_vs_Smyslov, EuwW_lostTo_Smy_MF)
H <- H + trial(  c("Ewue","MF")           , Ewue_vs_Smyslov, SmyW_lostTo_Euw_MF)
H <- H + trial(  c("draw","MF")            , Ewue_vs_Smyslov, EuwW_draws_Smy_MF)
H <- H + trial(  c("draw","MF")            , Ewue_vs_Smyslov, SmyW_draws_Euw_MF)

#Reshevsky VS Botvinnik
Reshevsky_vs_Botvinnik <- c("Reshevsky","Botvinnik","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Reshevsky"  ,"white"), Reshevsky_vs_Botvinnik, ResW_beats_Bot_NMF)
H <- H + trial(c("Botvinnik","white"), Reshevsky_vs_Botvinnik, BotW_beats_Res_NMF)
H <- H + trial(  "Botvinnik"           , Reshevsky_vs_Botvinnik, ResW_lostTo_Bot_NMF)
H <- H + trial(  "Reshevsky"           , Reshevsky_vs_Botvinnik, BotW_lostTo_Res_NMF)
H <- H + trial(  "draw"              , Reshevsky_vs_Botvinnik, ResW_draws_Bot_NMF)
H <- H + trial(  "draw"              , Reshevsky_vs_Botvinnik, BotW_draws_Res_NMF)

#MF
H <- H + trial(c("Reshevsky"  ,"white","MF"), Reshevsky_vs_Botvinnik, ResW_beats_Bot_MF)
H <- H + trial(c("Botvinnik","white","MF") , Reshevsky_vs_Botvinnik, BotW_beats_Res_MF)
H <- H + trial(  c("Botvinnik","MF")           , Reshevsky_vs_Botvinnik, ResW_lostTo_Bot_MF)
H <- H + trial(  c("Reshevsky","MF")           , Reshevsky_vs_Botvinnik, BotW_lostTo_Res_MF)
H <- H + trial(  c("draw","MF")            , Reshevsky_vs_Botvinnik, ResW_draws_Bot_MF)
H <- H + trial(  c("draw","MF")            , Reshevsky_vs_Botvinnik, BotW_draws_Res_MF)

#Botvinnik VS Keres
Botvinnik_vs_Keres <- c("Botvinnik","Keres","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Botvinnik"  ,"white"), Botvinnik_vs_Keres, BotW_beats_Ker_NMF)
H <- H + trial(c("Keres","white"), Botvinnik_vs_Keres, KerW_beats_Bot_NMF)
H <- H + trial(  "Keres"           , Botvinnik_vs_Keres, BotW_lostTo_Ker_NMF)
H <- H + trial(  "Botvinnik"           , Botvinnik_vs_Keres, KerW_lostTo_Bot_NMF)
H <- H + trial(  "draw"              , Botvinnik_vs_Keres, KerW_draws_Bot_NMF)
H <- H + trial(  "draw"              , Botvinnik_vs_Keres, BotW_draws_Ker_NMF)

#MF
H <- H + trial(c("Botvinnik"  ,"white","MF"), Botvinnik_vs_Keres, BotW_beats_Ker_MF)
H <- H + trial(c("Keres","white","MF") , Botvinnik_vs_Keres, KerW_beats_Bot_MF)
H <- H + trial(  c("Keres","MF")           , Botvinnik_vs_Keres, BotW_lostTo_Ker_MF)
H <- H + trial(  c("Botvinnik","MF")           , Botvinnik_vs_Keres, KerW_lostTo_Bot_MF)
H <- H + trial(  c("draw","MF")            , Botvinnik_vs_Keres, KerW_draws_Bot_MF)
H <- H + trial(  c("draw","MF")            , Botvinnik_vs_Keres, BotW_draws_Ker_MF)


#Reshevsky VS Keres
Reshevsky_vs_Keres <- c("Reshevsky","Keres","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Reshevsky"  ,"white"), Reshevsky_vs_Keres, ResW_beats_Ker_NMF)
H <- H + trial(c("Keres","white"), Reshevsky_vs_Keres, KerW_beats_Res_NMF)
H <- H + trial(  "Keres"           , Reshevsky_vs_Keres, ResW_lostTo_Ker_NMF)
H <- H + trial(  "Reshevsky"           , Reshevsky_vs_Keres, KerW_lostTo_Res_NMF)
H <- H + trial(  "draw"              , Reshevsky_vs_Keres, ResW_draws_Ker_NMF)
H <- H + trial(  "draw"              , Reshevsky_vs_Keres, KerW_draws_Res_NMF)

#MF
H <- H + trial(c("Reshevsky"  ,"white","MF"), Reshevsky_vs_Keres, ResW_beats_Ker_MF)
H <- H + trial(c("Keres","white","MF") , Reshevsky_vs_Keres, KerW_beats_Res_MF)
H <- H + trial(  c("Keres","MF")           , Reshevsky_vs_Keres, ResW_lostTo_Ker_MF)
H <- H + trial(  c("Reshevsky","MF")           , Reshevsky_vs_Keres, KerW_lostTo_Res_MF)
H <- H + trial(  c("draw","MF")            , Reshevsky_vs_Keres, ResW_draws_Ker_MF)
H <- H + trial(  c("draw","MF")            , Reshevsky_vs_Keres, KerW_draws_Res_MF)

detach(results)

Hyper_fide1948 <- H
Hyper_fide1948
(Hyper_fide1948_maxp <- maxp(Hyper_fide1948))

```


```{r}
sum(Hyper_fide1948_maxp)

names <- names(Hyper_fide1948_maxp)
results1948_df <- data.frame(Entity = names, Ranking = unique(Hyper_fide1948_maxp))
results1948_df

library(ggplot2)
ggplot(results1948_df, aes(Ranking,Entity))+ geom_point() + labs(title = "1948 World Championship ranking (w.r.t Mental Fatigue)")
```

##Hypothesis Testing

$H_0 : p_1 =... = p_n$

$H_1 : p_1 \neq... \neq p_n$

```{r}
test <- equalp.test(H)
test
```

The results above show a p-value = `r test$p.value` which is lower than a significance level of 0.05. This suggests that all the entities have different strengths.