---
title: "ChessMF"
author: "Toetu"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Here, I am analyzing the effects of Mental Fatigue (MF) on expert chess players during a game of chess. The data sets that we will be analyzing are the 1948 FIDE world chess championship, and the 2022 candidates games. We will be using the 'Hyper2' package developed by Dr. Hankin. 

```{r}
library(hyper2)
library(readxl)

#Data
Fide2022 <- read_excel("Fide2022.xlsx")
View(Fide2022)

#We have 5 players that played 50 games all together
#How many possible games of 2 can occur for 5 players?
factorial(8)/(factorial(8 - 2)*factorial(2))

```

#Hyper2 object
```{r}
fide22 <- c(
 #Nepo VS Ding 
  NepW_lostTo_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NepW_beats_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NepW_draws_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  DinW_lostTo_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DinW_beats_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DinW_draws_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NepW_lostTo_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NepW_beats_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NepW_draws_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  DinW_lostTo_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DinW_beats_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DinW_draws_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  
 #Nepo VS Radjabov 
  NepW_lostTo_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NepW_beats_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NepW_draws_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  RadW_lostTo_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RadW_beats_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RadW_draws_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NepW_lostTo_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NepW_beats_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NepW_draws_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  RadW_lostTo_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RadW_beats_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RadW_draws_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Nepo VS Nakamura 
  NepW_lostTo_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NepW_beats_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NepW_draws_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  NakW_lostTo_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NakW_beats_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NakW_draws_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NepW_lostTo_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NepW_beats_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NepW_draws_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  NakW_lostTo_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NakW_beats_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NakW_draws_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Nepo VS Caruana 
  NepW_lostTo_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NepW_beats_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NepW_draws_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  CarW_lostTo_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  CarW_beats_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  CarW_draws_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NepW_lostTo_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NepW_beats_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NepW_draws_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  CarW_lostTo_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  CarW_beats_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  CarW_draws_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Nepo VS Firouzja 
  NepW_lostTo_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NepW_beats_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NepW_draws_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  FirW_lostTo_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  FirW_beats_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  FirW_draws_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NepW_lostTo_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NepW_beats_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NepW_draws_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  FirW_lostTo_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  FirW_beats_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  FirW_draws_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Nepo VS Duda
  NepW_lostTo_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NepW_beats_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NepW_draws_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  DudW_lostTo_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DudW_beats_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DudW_draws_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NepW_lostTo_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NepW_beats_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NepW_draws_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  DudW_lostTo_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DudW_beats_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DudW_draws_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Nepo VS Rapport
  NepW_lostTo_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NepW_beats_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NepW_draws_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  RapW_lostTo_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RapW_beats_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RapW_draws_Nep_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NepW_lostTo_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NepW_beats_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NepW_draws_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nepo" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  RapW_lostTo_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RapW_beats_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RapW_draws_Nep_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nepo" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 
 #Ding VS Radjabov
  DinW_lostTo_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DinW_beats_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DinW_draws_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  RadW_lostTo_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RadW_beats_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RadW_draws_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  DinW_lostTo_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DinW_beats_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DinW_draws_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  RadW_lostTo_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RadW_beats_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RadW_draws_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Ding VS Nakamura
  DinW_lostTo_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DinW_beats_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DinW_draws_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  NakW_lostTo_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NakW_beats_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NakW_draws_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  DinW_lostTo_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DinW_beats_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DinW_draws_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  NakW_lostTo_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NakW_beats_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NakW_draws_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Ding VS Caruana
  DinW_lostTo_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DinW_beats_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DinW_draws_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  CarW_lostTo_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  CarW_beats_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  CarW_draws_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  DinW_lostTo_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DinW_beats_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DinW_draws_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  CarW_lostTo_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  CarW_beats_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  CarW_draws_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Ding VS Firouzja
  DinW_lostTo_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DinW_beats_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DinW_draws_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  FirW_lostTo_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  FirW_beats_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  FirW_draws_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  DinW_lostTo_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DinW_beats_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DinW_draws_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  FirW_lostTo_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  FirW_beats_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  FirW_draws_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Ding VS Duda
  DinW_lostTo_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DinW_beats_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DinW_draws_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  DudW_lostTo_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DudW_beats_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DudW_draws_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  DinW_lostTo_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DinW_beats_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DinW_draws_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  DudW_lostTo_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DudW_beats_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DudW_draws_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Ding VS Rapport
  DinW_lostTo_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DinW_beats_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DinW_draws_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  RapW_lostTo_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RapW_beats_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RapW_draws_Din_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  DinW_lostTo_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DinW_beats_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DinW_draws_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Ding" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  RapW_lostTo_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RapW_beats_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RapW_draws_Din_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Ding" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Radjabov VS Nakamura
  RadW_lostTo_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RadW_beats_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RadW_draws_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  NakW_lostTo_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NakW_beats_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NakW_draws_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  RadW_lostTo_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RadW_beats_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RadW_draws_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  NakW_lostTo_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NakW_beats_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NakW_draws_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Radjabov VS Caruana
  RadW_lostTo_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RadW_beats_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RadW_draws_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  CarW_lostTo_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  CarW_beats_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  CarW_draws_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  RadW_lostTo_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RadW_beats_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RadW_draws_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  CarW_lostTo_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  CarW_beats_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  CarW_draws_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Radjabov VS Firouzja
  RadW_lostTo_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RadW_beats_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RadW_draws_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  FirW_lostTo_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  FirW_beats_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  FirW_draws_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  RadW_lostTo_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RadW_beats_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RadW_draws_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  FirW_lostTo_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  FirW_beats_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  FirW_draws_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Radjabov VS Duda
  RadW_lostTo_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RadW_beats_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RadW_draws_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  DudW_lostTo_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DudW_beats_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DudW_draws_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  RadW_lostTo_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RadW_beats_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RadW_draws_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  DudW_lostTo_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DudW_beats_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DudW_draws_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Radjabov VS Rapport
  RadW_lostTo_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RadW_beats_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RadW_draws_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  RapW_lostTo_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RapW_beats_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RapW_draws_Rad_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  RadW_lostTo_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RadW_beats_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RadW_draws_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Radjabov" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  RapW_lostTo_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RapW_beats_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RapW_draws_Rad_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Radjabov" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Nakamura VS Caruana
  NakW_lostTo_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NakW_beats_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NakW_draws_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  CarW_lostTo_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  CarW_beats_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  CarW_draws_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NakW_lostTo_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NakW_beats_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NakW_draws_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  CarW_lostTo_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  CarW_beats_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  CarW_draws_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 
 #Nakamura VS Firouzja
  NakW_lostTo_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NakW_beats_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NakW_draws_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  FirW_lostTo_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  FirW_beats_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  FirW_draws_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NakW_lostTo_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NakW_beats_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NakW_draws_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  FirW_lostTo_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  FirW_beats_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  FirW_draws_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Nakamura VS Duda
  NakW_lostTo_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NakW_beats_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NakW_draws_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  DudW_lostTo_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DudW_beats_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DudW_draws_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NakW_lostTo_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NakW_beats_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NakW_draws_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  DudW_lostTo_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DudW_beats_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DudW_draws_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Nakamura VS Rapport
  NakW_lostTo_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  NakW_beats_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  NakW_draws_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  RapW_lostTo_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RapW_beats_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RapW_draws_Nak_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  NakW_lostTo_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  NakW_beats_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  NakW_draws_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Nakamura" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  RapW_lostTo_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RapW_beats_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RapW_draws_Nak_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Nakamura" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Caruana VS Firouzja
  CarW_lostTo_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  CarW_beats_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  CarW_draws_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  FirW_lostTo_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  FirW_beats_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  FirW_draws_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  CarW_lostTo_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  CarW_beats_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  CarW_draws_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  FirW_lostTo_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  FirW_beats_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  FirW_draws_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Caruana VS Duda
  CarW_lostTo_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  CarW_beats_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  CarW_draws_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  DudW_lostTo_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DudW_beats_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DudW_draws_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  CarW_lostTo_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  CarW_beats_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  CarW_draws_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  DudW_lostTo_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DudW_beats_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DudW_draws_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Caruana VS Rapport
  CarW_lostTo_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  CarW_beats_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  CarW_draws_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  RapW_lostTo_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RapW_beats_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RapW_draws_Car_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  CarW_lostTo_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  CarW_beats_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  CarW_draws_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Caruana" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  RapW_lostTo_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RapW_beats_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RapW_draws_Car_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Caruana" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Firouzja VS Duda
  FirW_lostTo_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  FirW_beats_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  FirW_draws_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  DudW_lostTo_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DudW_beats_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DudW_draws_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  FirW_lostTo_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  FirW_beats_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  FirW_draws_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  DudW_lostTo_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DudW_beats_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DudW_draws_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Firouzja VS Rapport
  FirW_lostTo_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  FirW_beats_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  FirW_draws_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  RapW_lostTo_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RapW_beats_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RapW_draws_Fir_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  FirW_lostTo_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  FirW_beats_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  FirW_draws_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Firouzja" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  RapW_lostTo_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RapW_beats_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RapW_draws_Fir_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Firouzja" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
 
 #Duda VS Rapport
  DudW_lostTo_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  DudW_beats_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  DudW_draws_Rap_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  RapW_lostTo_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves < 40,])[1],
  RapW_beats_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves < 40,])[1],
  RapW_draws_Dud_NMF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves < 40,])[1],
  
  DudW_lostTo_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  DudW_beats_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  DudW_draws_Rap_MF = dim(Fide2022[Fide2022$WhitePlayer == "Duda" & Fide2022$BlackPlayer== "Rapport" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1],
  RapW_lostTo_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0 & Fide2022$Moves >= 40,])[1],
  RapW_beats_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 1 & Fide2022$Moves >= 40,])[1],
  RapW_draws_Dud_MF = dim(Fide2022[Fide2022$WhitePlayer == "Rapport" & Fide2022$BlackPlayer== "Duda" & Fide2022$White == 0.5 & Fide2022$Moves >= 40,])[1]
)



```



**Hyper 2 object**
```{r}
results <- as.list(fide22)
attach(results)
H <- hyper2()

#Nepo VS Ding 
Nepo_vs_Ding <- c("Nepo","Ding","white","draw","MF")  # all "players", real and imaginary

#No MF
H <- H + trial(c("Nepo"  ,"white"), Nepo_vs_Ding, NepW_beats_Din_NMF)
H <- H + trial(c("Ding","white"), Nepo_vs_Ding, DinW_beats_Nep_NMF)
H <- H + trial(  "Ding"           , Nepo_vs_Ding, NepW_lostTo_Din_NMF)
H <- H + trial(  "Nepo"           , Nepo_vs_Ding, DinW_lostTo_Nep_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Ding, NepW_draws_Din_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Ding, DinW_draws_Nep_NMF)

#MF
H <- H + trial(c("Nepo"  ,"white","MF"), Nepo_vs_Ding, NepW_beats_Din_MF)
H <- H + trial(c("Ding","white","MF"), Nepo_vs_Ding, DinW_beats_Nep_MF)
H <- H + trial(  c("Ding","MF")           , Nepo_vs_Ding, NepW_lostTo_Din_MF)
H <- H + trial(  c("Nepo","MF")           , Nepo_vs_Ding, DinW_lostTo_Nep_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Ding, NepW_draws_Din_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Ding, DinW_draws_Nep_MF)

#Nepo VS Radjabov 
Nepo_vs_Radjabov <- c("Nepo","Radjabov","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nepo"  ,"white"), Nepo_vs_Radjabov, NepW_beats_Rad_NMF)
H <- H + trial(c("Radjabov","white"), Nepo_vs_Radjabov, RadW_beats_Nep_NMF)
H <- H + trial(  "Radjabov"           , Nepo_vs_Radjabov, NepW_lostTo_Rad_NMF)
H <- H + trial(  "Nepo"           , Nepo_vs_Radjabov, RadW_lostTo_Nep_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Radjabov, NepW_draws_Rad_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Radjabov, RadW_draws_Nep_NMF)

#MF
H <- H + trial(c("Nepo"  ,"white","MF"), Nepo_vs_Radjabov, NepW_beats_Rad_MF)
H <- H + trial(c("Radjabov","white","MF"), Nepo_vs_Radjabov, RadW_beats_Nep_MF)
H <- H + trial(  c("Radjabov","MF")           , Nepo_vs_Radjabov, NepW_lostTo_Rad_MF)
H <- H + trial(  c("Nepo","MF")           , Nepo_vs_Radjabov, RadW_lostTo_Nep_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Radjabov, NepW_draws_Rad_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Radjabov, RadW_draws_Nep_MF)

#Nepo VS Nakamura
Nepo_vs_Nakamura <- c("Nepo","Nakamura","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nepo"  ,"white"), Nepo_vs_Nakamura, NepW_beats_Nak_NMF)
H <- H + trial(c("Nakamura","white"), Nepo_vs_Nakamura, NakW_beats_Nep_NMF)
H <- H + trial(  "Nakamura"           , Nepo_vs_Nakamura, NepW_lostTo_Nak_NMF)
H <- H + trial(  "Nepo"           , Nepo_vs_Nakamura, NakW_lostTo_Nep_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Nakamura, NepW_draws_Nak_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Nakamura, NakW_draws_Nep_NMF)

#MF
H <- H + trial(c("Nepo"  ,"white","MF"), Nepo_vs_Nakamura, NepW_beats_Nak_MF)
H <- H + trial(c("Nakamura","white","MF"), Nepo_vs_Nakamura, NakW_beats_Nep_MF)
H <- H + trial(  c("Nakamura","MF")           , Nepo_vs_Nakamura, NepW_lostTo_Nak_MF)
H <- H + trial(  c("Nepo","MF")           , Nepo_vs_Nakamura, NakW_lostTo_Nep_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Nakamura, NepW_draws_Nak_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Nakamura, NakW_draws_Nep_MF)

#Nepo VS Caruana 
Nepo_vs_Caruana <- c("Nepo","Caruana","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nepo"  ,"white"), Nepo_vs_Caruana, NepW_beats_Car_NMF)
H <- H + trial(c("Caruana","white"), Nepo_vs_Caruana, CarW_beats_Nep_NMF)
H <- H + trial(  "Caruana"           , Nepo_vs_Caruana, NepW_lostTo_Car_NMF)
H <- H + trial(  "Nepo"           , Nepo_vs_Caruana, CarW_lostTo_Nep_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Caruana, NepW_draws_Car_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Caruana, CarW_draws_Nep_NMF)

#MF
H <- H + trial(c("Nepo"  ,"white","MF"), Nepo_vs_Caruana, NepW_beats_Car_MF)
H <- H + trial(c("Caruana","white","MF"), Nepo_vs_Caruana, CarW_beats_Nep_MF)
H <- H + trial(  c("Caruana","MF")           , Nepo_vs_Caruana, NepW_lostTo_Car_MF)
H <- H + trial(  c("Nepo","MF")           , Nepo_vs_Caruana, CarW_lostTo_Nep_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Caruana, NepW_draws_Car_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Caruana, CarW_draws_Nep_MF)

#Nepo VS Firouzja 
Nepo_vs_Firouzja <- c("Nepo","Firouzja","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nepo"  ,"white"), Nepo_vs_Firouzja, NepW_beats_Fir_NMF)
H <- H + trial(c("Firouzja","white"), Nepo_vs_Firouzja, FirW_beats_Nep_NMF)
H <- H + trial(  "Firouzja"           , Nepo_vs_Firouzja, NepW_lostTo_Fir_NMF)
H <- H + trial(  "Nepo"           , Nepo_vs_Firouzja, FirW_lostTo_Nep_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Firouzja, NepW_draws_Fir_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Firouzja, FirW_draws_Nep_NMF)

#MF
H <- H + trial(c("Nepo"  ,"white","MF"), Nepo_vs_Firouzja, NepW_beats_Fir_MF)
H <- H + trial(c("Firouzja","white","MF"), Nepo_vs_Firouzja, FirW_beats_Nep_MF)
H <- H + trial(  c("Firouzja","MF")           , Nepo_vs_Firouzja, NepW_lostTo_Fir_MF)
H <- H + trial(  c("Nepo","MF")           , Nepo_vs_Firouzja, FirW_lostTo_Nep_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Firouzja, NepW_draws_Fir_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Firouzja, FirW_draws_Nep_MF)

#Nepo VS Duda 
Nepo_vs_Firouzja <- c("Nepo","Duda","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nepo"  ,"white"), Nepo_vs_Firouzja, NepW_beats_Dud_NMF)
H <- H + trial(c("Duda","white"), Nepo_vs_Firouzja, DudW_beats_Nep_NMF)
H <- H + trial(  "Duda"           , Nepo_vs_Firouzja, NepW_lostTo_Dud_NMF)
H <- H + trial(  "Nepo"           , Nepo_vs_Firouzja, DudW_lostTo_Nep_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Firouzja, NepW_draws_Dud_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Firouzja, DudW_draws_Nep_NMF)

#MF
H <- H + trial(c("Nepo"  ,"white","MF"), Nepo_vs_Firouzja, NepW_beats_Dud_MF)
H <- H + trial(c("Duda","white","MF"), Nepo_vs_Firouzja, DudW_beats_Nep_MF)
H <- H + trial(  c("Duda","MF")           , Nepo_vs_Firouzja, NepW_lostTo_Dud_MF)
H <- H + trial(  c("Nepo","MF")           , Nepo_vs_Firouzja, DudW_lostTo_Nep_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Firouzja, NepW_draws_Dud_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Firouzja, DudW_draws_Nep_MF)

#Nepo VS Rapport 
Nepo_vs_Rapport <- c("Nepo","Rapport","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nepo"  ,"white"), Nepo_vs_Rapport, NepW_beats_Rap_NMF)
H <- H + trial(c("Rapport","white"), Nepo_vs_Rapport, RapW_beats_Nep_NMF)
H <- H + trial(  "Rapport"           , Nepo_vs_Rapport, NepW_lostTo_Rap_NMF)
H <- H + trial(  "Nepo"           , Nepo_vs_Rapport, RapW_lostTo_Nep_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Rapport, NepW_draws_Rap_NMF)
H <- H + trial(  "draw"             , Nepo_vs_Rapport, RapW_draws_Nep_NMF)

#MF
H <- H + trial(c("Nepo"  ,"white","MF"), Nepo_vs_Rapport, NepW_beats_Rap_MF)
H <- H + trial(c("Rapport","white","MF"), Nepo_vs_Rapport, RapW_beats_Nep_MF)
H <- H + trial(  c("Rapport","MF")           , Nepo_vs_Rapport, NepW_lostTo_Rap_MF)
H <- H + trial(  c("Nepo","MF")           , Nepo_vs_Rapport, RapW_lostTo_Nep_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Rapport, NepW_draws_Rap_MF)
H <- H + trial(  c("draw","MF")            , Nepo_vs_Rapport, RapW_draws_Nep_MF)

#Ding VS Radjabov
Ding_vs_Radjabov <- c("Ding","Radjabov","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Ding"  ,"white"), Ding_vs_Radjabov, DinW_beats_Rad_NMF)
H <- H + trial(c("Radjabov","white"), Ding_vs_Radjabov, RadW_beats_Din_NMF)
H <- H + trial(  "Radjabov"           , Ding_vs_Radjabov, DinW_lostTo_Rad_NMF)
H <- H + trial(  "Ding"           , Ding_vs_Radjabov, RadW_lostTo_Din_NMF)
H <- H + trial(  "draw"             , Ding_vs_Radjabov, DinW_draws_Rad_NMF)
H <- H + trial(  "draw"             , Ding_vs_Radjabov, RapW_draws_Din_NMF)

#MF
H <- H + trial(c("Ding"  ,"white","MF"), Ding_vs_Radjabov, DinW_beats_Rad_MF)
H <- H + trial(c("Radjabov","white","MF"), Ding_vs_Radjabov, RadW_beats_Din_MF)
H <- H + trial(  c("Radjabov","MF")           , Ding_vs_Radjabov, DinW_lostTo_Rad_MF)
H <- H + trial(  c("Ding","MF")           , Ding_vs_Radjabov, RadW_lostTo_Din_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Radjabov, DinW_draws_Rad_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Radjabov, RadW_draws_Din_MF)

#Ding VS Nakamura
Ding_vs_Nakamura <- c("Ding","Nakamura","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Ding"  ,"white"), Ding_vs_Nakamura, DinW_beats_Nak_NMF)
H <- H + trial(c("Nakamura","white"), Ding_vs_Nakamura, NakW_beats_Din_NMF)
H <- H + trial(  "Nakamura"           , Ding_vs_Nakamura, DinW_lostTo_Nak_NMF)
H <- H + trial(  "Ding"           , Ding_vs_Nakamura, NakW_lostTo_Din_NMF)
H <- H + trial(  "draw"             , Ding_vs_Nakamura, DinW_draws_Nak_NMF)
H <- H + trial(  "draw"             , Ding_vs_Nakamura, NakW_draws_Din_NMF)

#MF
H <- H + trial(c("Ding"  ,"white","MF"), Ding_vs_Nakamura, DinW_beats_Nak_MF)
H <- H + trial(c("Nakamura","white","MF"), Ding_vs_Nakamura, NakW_beats_Din_MF)
H <- H + trial(  c("Nakamura","MF")           , Ding_vs_Nakamura, DinW_lostTo_Nak_MF)
H <- H + trial(  c("Ding","MF")           , Ding_vs_Nakamura, NakW_lostTo_Din_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Nakamura, DinW_draws_Nak_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Nakamura, RadW_draws_Din_MF)

#Ding VS Caruana
Ding_vs_Caruana <- c("Ding","Caruana","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Ding"  ,"white"), Ding_vs_Caruana, DinW_beats_Car_NMF)
H <- H + trial(c("Caruana","white"), Ding_vs_Caruana, CarW_beats_Din_NMF)
H <- H + trial(  "Caruana"           , Ding_vs_Caruana, DinW_lostTo_Car_NMF)
H <- H + trial(  "Ding"           , Ding_vs_Caruana, CarW_lostTo_Din_NMF)
H <- H + trial(  "draw"             , Ding_vs_Caruana, DinW_draws_Car_NMF)
H <- H + trial(  "draw"             , Ding_vs_Caruana, CarW_draws_Din_NMF)

#MF
H <- H + trial(c("Ding"  ,"white","MF"), Ding_vs_Caruana, DinW_beats_Car_MF)
H <- H + trial(c("Caruana","white","MF"), Ding_vs_Caruana, CarW_beats_Din_MF)
H <- H + trial(  c("Caruana","MF")           , Ding_vs_Caruana, DinW_lostTo_Car_MF)
H <- H + trial(  c("Ding","MF")           , Ding_vs_Caruana, CarW_lostTo_Din_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Caruana, DinW_draws_Car_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Caruana, CarW_draws_Din_MF)

#Ding VS Firouzja
Ding_vs_Firouzja <- c("Ding","Firouzja","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Ding"  ,"white"), Ding_vs_Firouzja, DinW_beats_Fir_NMF)
H <- H + trial(c("Firouzja","white"), Ding_vs_Firouzja, FirW_beats_Din_NMF)
H <- H + trial(  "Firouzja"           , Ding_vs_Firouzja, DinW_lostTo_Fir_NMF)
H <- H + trial(  "Ding"           , Ding_vs_Firouzja, FirW_lostTo_Din_NMF)
H <- H + trial(  "draw"             , Ding_vs_Firouzja, DinW_draws_Fir_NMF)
H <- H + trial(  "draw"             , Ding_vs_Firouzja, FirW_draws_Din_NMF)

#MF
H <- H + trial(c("Ding"  ,"white","MF"), Ding_vs_Firouzja, DinW_beats_Fir_MF)
H <- H + trial(c("Firouzja","white","MF"), Ding_vs_Firouzja, FirW_beats_Din_MF)
H <- H + trial(  c("Firouzja","MF")           , Ding_vs_Firouzja, DinW_lostTo_Fir_MF)
H <- H + trial(  c("Ding","MF")           , Ding_vs_Firouzja, FirW_lostTo_Din_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Firouzja, DinW_draws_Fir_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Firouzja, FirW_draws_Din_MF)

#Ding VS Duda
Ding_vs_Duda <- c("Ding","Duda","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Ding"  ,"white"), Ding_vs_Duda, DinW_beats_Dud_NMF)
H <- H + trial(c("Duda","white"), Ding_vs_Duda, DudW_beats_Din_NMF)
H <- H + trial(  "Duda"           , Ding_vs_Duda, DinW_lostTo_Dud_NMF)
H <- H + trial(  "Ding"           , Ding_vs_Duda, DudW_lostTo_Din_NMF)
H <- H + trial(  "draw"             , Ding_vs_Duda, DinW_draws_Dud_NMF)
H <- H + trial(  "draw"             , Ding_vs_Duda, DudW_draws_Din_NMF)

#MF
H <- H + trial(c("Ding"  ,"white","MF"), Ding_vs_Duda, DinW_beats_Dud_MF)
H <- H + trial(c("Duda","white","MF"), Ding_vs_Duda, DudW_beats_Din_MF)
H <- H + trial(  c("Duda","MF")           , Ding_vs_Duda, DinW_lostTo_Dud_MF)
H <- H + trial(  c("Ding","MF")           , Ding_vs_Duda, DudW_lostTo_Din_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Duda, DinW_draws_Dud_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Duda, DudW_draws_Din_MF)

#Ding VS Rapport
Ding_vs_Rapport <- c("Ding","Rapport","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Ding"  ,"white"), Ding_vs_Rapport, DinW_beats_Rap_NMF)
H <- H + trial(c("Rapport","white"), Ding_vs_Rapport, RapW_beats_Din_NMF)
H <- H + trial(  "Rapport"           , Ding_vs_Rapport, DinW_lostTo_Rap_NMF)
H <- H + trial(  "Ding"           , Ding_vs_Rapport, RapW_lostTo_Din_NMF)
H <- H + trial(  "draw"             , Ding_vs_Rapport, DinW_draws_Rap_NMF)
H <- H + trial(  "draw"             , Ding_vs_Rapport, RapW_draws_Din_NMF)

#MF
H <- H + trial(c("Ding"  ,"white","MF"), Ding_vs_Rapport, DinW_beats_Rap_MF)
H <- H + trial(c("Rapport","white","MF"), Ding_vs_Rapport, RapW_beats_Din_MF)
H <- H + trial(  c("Rapport","MF")           , Ding_vs_Rapport, DinW_lostTo_Rap_MF)
H <- H + trial(  c("Ding","MF")           , Ding_vs_Rapport, RapW_lostTo_Din_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Rapport, DinW_draws_Rap_MF)
H <- H + trial(  c("draw","MF")            , Ding_vs_Rapport, RapW_draws_Din_MF)


#Radjabov VS Nakamura
Radjabov_vs_Nakamura <- c("Radjabov","Nakamura","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Radjabov" ,"white"), Radjabov_vs_Nakamura, RadW_beats_Nak_NMF)
H <- H + trial(c("Nakamura","white"), Radjabov_vs_Nakamura, NakW_beats_Rad_NMF)
H <- H + trial(  "Nakamura"           , Radjabov_vs_Nakamura, RadW_lostTo_Nak_NMF)
H <- H + trial(  "Radjabov"           , Radjabov_vs_Nakamura, NakW_lostTo_Rad_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Nakamura, RadW_draws_Nak_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Nakamura, NakW_draws_Rad_NMF)

#MF
H <- H + trial(c("Radjabov"  ,"white","MF"), Radjabov_vs_Nakamura, RadW_beats_Nak_MF)
H <- H + trial(c("Nakamura","white","MF"), Radjabov_vs_Nakamura, NakW_beats_Rad_MF)
H <- H + trial(  c("Nakamura","MF")           , Radjabov_vs_Nakamura, RadW_lostTo_Nak_MF)
H <- H + trial(  c("Radjabov","MF")           , Radjabov_vs_Nakamura, NakW_lostTo_Rad_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Nakamura, RadW_draws_Nak_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Nakamura, NakW_draws_Rad_MF)

#Radjabov VS Caruana
Radjabov_vs_Caruana <- c("Radjabov","Caruana","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Radjabov"  ,"white"), Radjabov_vs_Caruana, RadW_beats_Car_NMF)
H <- H + trial(c("Caruana","white"), Radjabov_vs_Caruana, CarW_beats_Rad_NMF)
H <- H + trial(  "Caruana"           , Radjabov_vs_Caruana, RadW_lostTo_Car_NMF)
H <- H + trial(  "Radjabov"           , Radjabov_vs_Caruana, CarW_lostTo_Rad_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Caruana, RadW_draws_Car_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Caruana, CarW_draws_Rad_NMF)

#MF
H <- H + trial(c("Radjabov"  ,"white","MF"), Radjabov_vs_Caruana, RadW_beats_Car_MF)
H <- H + trial(c("Caruana","white","MF"), Radjabov_vs_Caruana, CarW_beats_Rad_MF)
H <- H + trial(  c("Caruana","MF")           , Radjabov_vs_Caruana, RadW_lostTo_Car_MF)
H <- H + trial(  c("Radjabov","MF")           , Radjabov_vs_Caruana, CarW_lostTo_Rad_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Caruana, RadW_draws_Car_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Caruana, CarW_draws_Rad_MF)

#Radjabov VS Firouzja
Radjabov_vs_Firouzja <- c("Radjabov","Firouzja","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Radjabov"  ,"white"), Radjabov_vs_Firouzja, RadW_beats_Fir_NMF)
H <- H + trial(c("Firouzja","white"), Radjabov_vs_Firouzja, FirW_beats_Rad_NMF)
H <- H + trial(  "Firouzja"           , Radjabov_vs_Firouzja, RadW_lostTo_Fir_NMF)
H <- H + trial(  "Radjabov"           , Radjabov_vs_Firouzja, FirW_lostTo_Rad_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Firouzja, RadW_draws_Fir_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Firouzja, FirW_draws_Rad_NMF)

#MF
H <- H + trial(c("Radjabov"  ,"white","MF"), Radjabov_vs_Firouzja, RadW_beats_Fir_MF)
H <- H + trial(c("Firouzja","white","MF"), Radjabov_vs_Firouzja, FirW_beats_Rad_MF)
H <- H + trial(  c("Firouzja","MF")           , Radjabov_vs_Firouzja, RadW_lostTo_Fir_MF)
H <- H + trial(  c("Radjabov","MF")           , Radjabov_vs_Firouzja, FirW_lostTo_Rad_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Firouzja, RadW_draws_Fir_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Firouzja, FirW_draws_Rad_MF)

#Radjabov VS Duda
Radjabov_vs_Duda <- c("Radjabov","Duda","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Radjabov"  ,"white"), Radjabov_vs_Duda, RadW_beats_Dud_NMF)
H <- H + trial(c("Duda","white"), Radjabov_vs_Duda, DudW_beats_Rad_NMF)
H <- H + trial(  "Duda"           , Radjabov_vs_Duda, RadW_lostTo_Dud_NMF)
H <- H + trial(  "Radjabov"           , Radjabov_vs_Duda, DudW_lostTo_Rad_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Duda, RadW_draws_Dud_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Duda, DudW_draws_Rad_NMF)

#MF
H <- H + trial(c("Radjabov"  ,"white","MF"), Radjabov_vs_Duda, RadW_beats_Dud_MF)
H <- H + trial(c("Duda","white","MF"), Radjabov_vs_Duda, DudW_beats_Rad_MF)
H <- H + trial(  c("Duda","MF")           , Radjabov_vs_Duda, RadW_lostTo_Dud_MF)
H <- H + trial(  c("Radjabov","MF")           , Radjabov_vs_Duda, DudW_lostTo_Rad_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Duda, RadW_draws_Dud_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Duda, DudW_draws_Rad_MF)

#Radjabov VS Rapport
Radjabov_vs_Rapport <- c("Radjabov","Rapport","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Radjabov"  ,"white"), Radjabov_vs_Rapport, RadW_beats_Rap_NMF)
H <- H + trial(c("Rapport","white"), Radjabov_vs_Rapport, RapW_beats_Rad_NMF)
H <- H + trial(  "Rapport"           , Radjabov_vs_Rapport, RadW_lostTo_Rap_NMF)
H <- H + trial(  "Radjabov"           , Radjabov_vs_Rapport, RapW_lostTo_Rad_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Rapport, RadW_draws_Rap_NMF)
H <- H + trial(  "draw"             , Radjabov_vs_Rapport, RapW_draws_Rad_NMF)

#MF
H <- H + trial(c("Radjabov"  ,"white","MF"), Radjabov_vs_Rapport, RadW_beats_Rap_MF)
H <- H + trial(c("Rapport","white","MF"), Radjabov_vs_Rapport, RapW_beats_Rad_MF)
H <- H + trial(  c("Rapport","MF")           , Radjabov_vs_Rapport, RadW_lostTo_Rap_MF)
H <- H + trial(  c("Radjabov","MF")           , Radjabov_vs_Rapport, RapW_lostTo_Rad_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Rapport, RadW_draws_Rap_MF)
H <- H + trial(  c("draw","MF")            , Radjabov_vs_Rapport, RapW_draws_Rad_MF)


#Nakamura VS Caruana
Nakamura_vs_Caruana <- c("Nakamura","Caruana","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nakamura"  ,"white"), Nakamura_vs_Caruana, NakW_beats_Car_NMF)
H <- H + trial(c("Caruana","white"), Nakamura_vs_Caruana, CarW_beats_Nak_NMF)
H <- H + trial(  "Caruana"           , Nakamura_vs_Caruana, NakW_lostTo_Car_NMF)
H <- H + trial(  "Nakamura"           , Nakamura_vs_Caruana, CarW_lostTo_Nak_NMF)
H <- H + trial(  "draw"             , Nakamura_vs_Caruana, NakW_draws_Car_NMF)
H <- H + trial(  "draw"             , Nakamura_vs_Caruana, CarW_draws_Nak_NMF)

#MF
H <- H + trial(c("Nakamura"  ,"white","MF"), Nakamura_vs_Caruana, NakW_beats_Car_MF)
H <- H + trial(c("Caruana","white","MF"), Nakamura_vs_Caruana, CarW_beats_Nak_MF)
H <- H + trial(  c("Caruana","MF")           , Nakamura_vs_Caruana, NakW_lostTo_Car_MF)
H <- H + trial(  c("Nakamura","MF")           , Nakamura_vs_Caruana, CarW_lostTo_Nak_MF)
H <- H + trial(  c("draw","MF")            , Nakamura_vs_Caruana, NakW_draws_Car_MF)
H <- H + trial(  c("draw","MF")            , Nakamura_vs_Caruana, CarW_draws_Nak_MF)

#Nakamura VS Firouzja
Nakamura_vs_Firouzja <- c("Nakamura","Firouzja","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nakamura"  ,"white"), Nakamura_vs_Firouzja, NakW_beats_Fir_NMF)
H <- H + trial(c("Firouzja","white"), Nakamura_vs_Firouzja, FirW_beats_Nak_NMF)
H <- H + trial(  "Firouzja"           , Nakamura_vs_Firouzja, NakW_lostTo_Fir_NMF)
H <- H + trial(  "Nakamura"           , Nakamura_vs_Firouzja, FirW_lostTo_Nak_NMF)
H <- H + trial(  "draw"             , Nakamura_vs_Firouzja, NakW_draws_Fir_NMF)
H <- H + trial(  "draw"             , Nakamura_vs_Firouzja, FirW_draws_Nak_NMF)

#MF
H <- H + trial(c("Nakamura"  ,"white","MF"), Nakamura_vs_Firouzja, NakW_beats_Fir_MF)
H <- H + trial(c("Firouzja","white","MF"), Nakamura_vs_Firouzja, FirW_beats_Nak_MF)
H <- H + trial(  c("Firouzja","MF")           , Nakamura_vs_Firouzja, NakW_lostTo_Fir_MF)
H <- H + trial(  c("Nakamura","MF")           , Nakamura_vs_Firouzja, FirW_lostTo_Nak_MF)
H <- H + trial(  c("draw","MF")            , Nakamura_vs_Firouzja, NakW_draws_Fir_MF)
H <- H + trial(  c("draw","MF")            , Nakamura_vs_Firouzja, FirW_draws_Nak_MF)

#Nakamura VS Duda
Nakamura_vs_Duda <- c("Nakamura","Duda","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nakamura"  ,"white"), Nakamura_vs_Duda, NakW_beats_Dud_NMF)
H <- H + trial(c("Duda","white"), Nakamura_vs_Duda, DudW_beats_Nak_NMF)
H <- H + trial(  "Duda"           , Nakamura_vs_Duda, NakW_lostTo_Dud_NMF)
H <- H + trial(  "Nakamura"           , Nakamura_vs_Duda, DudW_lostTo_Nak_NMF)
H <- H + trial(  "draw"             , Nakamura_vs_Duda, NakW_draws_Dud_NMF)
H <- H + trial(  "draw"             , Nakamura_vs_Duda, DudW_draws_Nak_NMF)

#MF
H <- H + trial(c("Nakamura"  ,"white","MF"), Nakamura_vs_Duda, NakW_beats_Dud_MF)
H <- H + trial(c("Duda","white","MF"), Nakamura_vs_Duda, DudW_beats_Nak_MF)
H <- H + trial(  c("Duda","MF")           , Nakamura_vs_Duda, NakW_lostTo_Dud_MF)
H <- H + trial(  c("Nakamura","MF")           , Nakamura_vs_Duda, DudW_lostTo_Nak_MF)
H <- H + trial(  c("draw","MF")            , Nakamura_vs_Duda, NakW_draws_Dud_MF)
H <- H + trial(  c("draw","MF")            , Nakamura_vs_Duda, DudW_draws_Nak_MF)

#Nakamura VS Rapport
Nakamura_vs_Rapport <- c("Nakamura","Rapport","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Nakamura"  ,"white"), Nakamura_vs_Rapport, NakW_beats_Rap_NMF)
H <- H + trial(c("Rapport","white"), Nakamura_vs_Rapport, RapW_beats_Nak_NMF)
H <- H + trial(  "Rapport"           , Nakamura_vs_Rapport, NakW_lostTo_Rap_NMF)
H <- H + trial(  "Nakamura"           , Nakamura_vs_Rapport, RapW_lostTo_Nak_NMF)
H <- H + trial(  "draw"             , Nakamura_vs_Rapport, NakW_draws_Rap_NMF)
H <- H + trial(  "draw"             , Nakamura_vs_Rapport, RapW_draws_Nak_NMF)

#MF
H <- H + trial(c("Nakamura"  ,"white","MF"), Nakamura_vs_Rapport, NakW_beats_Rap_MF)
H <- H + trial(c("Rapport","white","MF"), Nakamura_vs_Rapport, RapW_beats_Nak_MF)
H <- H + trial(  c("Rapport","MF")           , Nakamura_vs_Rapport, NakW_lostTo_Rap_MF)
H <- H + trial(  c("Nakamura","MF")           , Nakamura_vs_Rapport, RapW_lostTo_Nak_MF)
H <- H + trial(  c("draw","MF")            , Nakamura_vs_Rapport, NakW_draws_Rap_MF)
H <- H + trial(  c("draw","MF")            , Nakamura_vs_Rapport, RapW_draws_Nak_MF)

#Caruana VS Firouzja
Caruana_vs_Firouzja <- c("Caruana","Firouzja","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Caruana"  ,"white"), Caruana_vs_Firouzja, CarW_beats_Fir_NMF)
H <- H + trial(c("Firouzja","white"), Caruana_vs_Firouzja, FirW_beats_Car_NMF)
H <- H + trial(  "Firouzja"           , Caruana_vs_Firouzja, CarW_lostTo_Fir_NMF)
H <- H + trial(  "Caruana"           , Caruana_vs_Firouzja, FirW_lostTo_Car_NMF)
H <- H + trial(  "draw"             , Caruana_vs_Firouzja, CarW_draws_Fir_NMF)
H <- H + trial(  "draw"             , Caruana_vs_Firouzja, FirW_draws_Car_NMF)

#MF
H <- H + trial(c("Caruana"  ,"white","MF"), Caruana_vs_Firouzja, CarW_beats_Fir_MF)
H <- H + trial(c("Firouzja","white","MF"), Caruana_vs_Firouzja, FirW_beats_Car_MF)
H <- H + trial(  c("Firouzja","MF")           , Caruana_vs_Firouzja, CarW_lostTo_Fir_MF)
H <- H + trial(  c("Caruana","MF")           , Caruana_vs_Firouzja, FirW_lostTo_Car_MF)
H <- H + trial(  c("draw","MF")            , Caruana_vs_Firouzja, CarW_draws_Fir_MF)
H <- H + trial(  c("draw","MF")            , Caruana_vs_Firouzja, FirW_draws_Car_MF)

#Caruana VS Duda
Caruana_vs_Duda <- c("Caruana","Duda","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Caruana"  ,"white"), Caruana_vs_Duda, CarW_beats_Dud_NMF)
H <- H + trial(c("Duda","white"), Caruana_vs_Duda, DudW_beats_Car_NMF)
H <- H + trial(  "Duda"           , Caruana_vs_Duda, CarW_lostTo_Dud_NMF)
H <- H + trial(  "Caruana"           , Caruana_vs_Duda, DudW_lostTo_Car_NMF)
H <- H + trial(  "draw"             , Caruana_vs_Duda, CarW_draws_Dud_NMF)
H <- H + trial(  "draw"             , Caruana_vs_Duda, DudW_draws_Car_NMF)

#MF
H <- H + trial(c("Caruana"  ,"white","MF"), Caruana_vs_Duda, CarW_beats_Dud_MF)
H <- H + trial(c("Duda","white","MF"), Caruana_vs_Duda, DudW_beats_Car_MF)
H <- H + trial(  c("Duda","MF")           , Caruana_vs_Duda, CarW_lostTo_Dud_MF)
H <- H + trial(  c("Caruana","MF")           , Caruana_vs_Duda, DudW_lostTo_Car_MF)
H <- H + trial(  c("draw","MF")            , Caruana_vs_Duda, CarW_draws_Dud_MF)
H <- H + trial(  c("draw","MF")            , Caruana_vs_Duda, DudW_draws_Car_MF)

#Caruana VS Rapport
Caruana_vs_Rapport <- c("Caruana","Rapport","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Caruana"  ,"white"), Caruana_vs_Rapport, CarW_beats_Rap_NMF)
H <- H + trial(c("Rapport","white"), Caruana_vs_Rapport, RapW_beats_Car_NMF)
H <- H + trial(  "Rapport"           , Caruana_vs_Rapport, CarW_lostTo_Rap_NMF)
H <- H + trial(  "Caruana"           , Caruana_vs_Rapport, RapW_lostTo_Car_NMF)
H <- H + trial(  "draw"             , Caruana_vs_Rapport, CarW_draws_Rap_NMF)
H <- H + trial(  "draw"             , Caruana_vs_Rapport, RapW_draws_Car_NMF)

#MF
H <- H + trial(c("Caruana"  ,"white","MF"), Caruana_vs_Rapport, CarW_beats_Rap_MF)
H <- H + trial(c("Rapport","white","MF"), Caruana_vs_Rapport, RapW_beats_Car_MF)
H <- H + trial(  c("Rapport","MF")           , Caruana_vs_Rapport, CarW_lostTo_Rap_MF)
H <- H + trial(  c("Caruana","MF")           , Caruana_vs_Rapport, RapW_lostTo_Car_MF)
H <- H + trial(  c("draw","MF")            , Caruana_vs_Rapport, CarW_draws_Rap_MF)
H <- H + trial(  c("draw","MF")            , Caruana_vs_Rapport, RapW_draws_Car_MF)

#Firouzja VS Duda
Firouzja_vs_Duda <- c("Firouzja","Duda","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Firouzja"  ,"white"), Firouzja_vs_Duda, FirW_beats_Dud_NMF)
H <- H + trial(c("Duda","white"), Firouzja_vs_Duda, DudW_beats_Fir_NMF)
H <- H + trial(  "Duda"           , Firouzja_vs_Duda, FirW_lostTo_Dud_NMF)
H <- H + trial(  "Firouzja"           , Firouzja_vs_Duda, DudW_lostTo_Fir_NMF)
H <- H + trial(  "draw"             , Firouzja_vs_Duda, FirW_draws_Dud_NMF)
H <- H + trial(  "draw"             , Firouzja_vs_Duda, DudW_draws_Fir_NMF)

#MF
H <- H + trial(c("Firouzja"  ,"white","MF"), Firouzja_vs_Duda, FirW_beats_Dud_MF)
H <- H + trial(c("Duda","white","MF"), Firouzja_vs_Duda, DudW_beats_Fir_MF)
H <- H + trial(  c("Duda","MF")           , Firouzja_vs_Duda, FirW_lostTo_Dud_MF)
H <- H + trial(  c("Firouzja","MF")           , Firouzja_vs_Duda, DudW_lostTo_Fir_MF)
H <- H + trial(  c("draw","MF")            , Firouzja_vs_Duda, FirW_draws_Dud_MF)
H <- H + trial(  c("draw","MF")            , Firouzja_vs_Duda, DudW_draws_Fir_MF)

#Firouzja VS Rapport
Firouzja_vs_Rapport <- c("Firouzja","Rapport","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Firouzja"  ,"white"), Firouzja_vs_Rapport, FirW_beats_Rap_NMF)
H <- H + trial(c("Rapport","white"), Firouzja_vs_Rapport, RapW_beats_Fir_NMF)
H <- H + trial(  "Rapport"           , Firouzja_vs_Rapport, FirW_lostTo_Rap_NMF)
H <- H + trial(  "Firouzja"           , Firouzja_vs_Rapport, RapW_lostTo_Fir_NMF)
H <- H + trial(  "draw"             , Firouzja_vs_Rapport, FirW_draws_Rap_NMF)
H <- H + trial(  "draw"             , Firouzja_vs_Rapport, RapW_draws_Fir_NMF)

#MF
H <- H + trial(c("Firouzja"  ,"white","MF"), Firouzja_vs_Rapport, FirW_beats_Rap_MF)
H <- H + trial(c("Rapport","white","MF"), Firouzja_vs_Rapport, RapW_beats_Fir_MF)
H <- H + trial(  c("Rapport","MF")           , Firouzja_vs_Rapport, FirW_lostTo_Rap_MF)
H <- H + trial(  c("Firouzja","MF")           , Firouzja_vs_Rapport, RapW_lostTo_Fir_MF)
H <- H + trial(  c("draw","MF")            , Firouzja_vs_Rapport, FirW_draws_Rap_MF)
H <- H + trial(  c("draw","MF")            , Firouzja_vs_Rapport, RapW_draws_Fir_MF)

#Duda VS Rapport
Duda_vs_Rapport <- c("Duda","Rapport","white","draw","MF")  # all "players", real and imaginary

H <- H + trial(c("Duda"  ,"white"), Duda_vs_Rapport, DudW_beats_Rap_NMF)
H <- H + trial(c("Rapport","white"), Duda_vs_Rapport, RapW_beats_Dud_NMF)
H <- H + trial(  "Rapport"           , Duda_vs_Rapport, DudW_lostTo_Rap_NMF)
H <- H + trial(  "Duda"           , Duda_vs_Rapport, RapW_lostTo_Dud_NMF)
H <- H + trial(  "draw"             , Duda_vs_Rapport, DudW_draws_Rap_NMF)
H <- H + trial(  "draw"             , Duda_vs_Rapport, RapW_draws_Dud_NMF)

#MF
H <- H + trial(c("Duda"  ,"white","MF"), Duda_vs_Rapport, DudW_beats_Rap_MF)
H <- H + trial(c("Rapport","white","MF"), Duda_vs_Rapport, RapW_beats_Dud_MF)
H <- H + trial(  c("Rapport","MF")           , Duda_vs_Rapport, DudW_lostTo_Rap_MF)
H <- H + trial(  c("Duda","MF")           , Duda_vs_Rapport, RapW_lostTo_Dud_MF)
H <- H + trial(  c("draw","MF")            , Duda_vs_Rapport, DudW_draws_Rap_MF)
H <- H + trial(  c("draw","MF")            , Duda_vs_Rapport, RapW_draws_Dud_MF)

detach(results)

Hyper_Fide2022 <- H
Hyper_Fide2022
(Hyper_Fide2022_maxp <- maxp(Hyper_Fide2022))

```


```{r}
sum(Hyper_Fide2022_maxp)

names <- names(Hyper_Fide2022_maxp)
results2022_df <- data.frame(Entity = names, Ranking = unique(Hyper_Fide2022_maxp))
results2022_df

library(ggplot2)
ggplot(results2022_df, aes(Ranking,Entity))+ geom_point() + labs(title = "2022 World Candidates Tournament ranking (w.r.t Mental Fatigue)")  + geom_text(aes(label = round(Ranking,3)), nudge_x = 0.01, nudge_y = 0.3, size = 3)
```

##Hypothesis Testing

$H_0 : p_1 =... = p_n$

$H_1 : p_1 \neq... \neq p_n$

```{r}
test <- equalp.test(H)
test
```

The results above show a p-value = `r test$p.value` which is lower than a significance level of 0.05. This suggests that all the entities have different strengths.

Now, we should consider testing for the existence of the fatigue monster.

$H_0 : \mathfrak{F} \leq 0$
$H_1 : \mathfrak{F} > 0$

```{r, cache=TRUE}
gt <- specificp.gt.test(Hyper_Fide2022, "MF", 0); gt
lt <- specificp.lt.test(Hyper_Fide2022, "MF", 0); lt
```


```{r}
gt$null_hypothesis; lt$null_hypothesis 
```

